---
title: "Michael McCarthy, PhD"
#output:
#  pdf_document: default
  #word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(fontawesome)
library(gt)
library(readxl)

source('CV_lists.R')

```

### Contact Info

email - [mikem\@radicalresearch.llc](mailto:mikem@radicalresearch.llc){.email} github - [github.com/RadicalResearchLLC](https://github.com/RadicalResearchLLC) linkedin - [LinkedIn](https://www.linkedin.com/in/mike-mccarthy-7966964/)

## Summary

Founder and Chief Scientist at the environmental consulting firm **Radical Research, LLC**. Adjunct Professor of Environmental Analysis at [Pitzer College](https://www.pitzer.edu/). Vice-chair of [Riverside Neighbors Opposing Warehouses](https://sites.google.com/view/rivnow/). I have 25 years of experience as an atmospheric scientist, 20 years of experience as an environmental consultant, and a little over a year of experience as a community activist and professor.

My atmospheric science expertise includes near-road pollution gradients, health-risk assessments, spatio-temporal variability, source apportionment, emissions characterization, climate change, air toxics, and isotopic compositions. I typically apply statistical analysis and geospatial visualization methods to quantify and characterize air quality issues. I also develop custom applications for the display and visualization of large and complex datasets.

<hr>

## Work {.domain-header}

#### Experience

```{r, fig.align ='left'}
work |> 
  #filter(Academic == 'No') |>
  mutate(Time = glue::glue("{startMonth} {startYear} -- {endMonth} {endYear}",.na = '')) |> 
  select(title, organization, where, Time) |> 
    rename(Title = title, Organization = organization, Where = where) |> 
    gt() |> 
     opt_table_font(font = 'sans-serif', weight = 8) |> 
      tab_options(table.align = 'left',
                 table.font.size = '90%')

```

<hr>

#### Skills

```{r}

skills |> 
    rename(Domain = area, Skills = skills) |> 
    gt() |> 
     opt_table_font(font = 'sans-serif', weight = 24) |> 
     tab_options(table.align = 'left',
                 table.font.size = '90%')#,
  #               container.width = 400)

```

<hr>

## Academia {.domain-header}

#### Education

```{r}

edu |> 
  filter(resume == 1) |> 
  mutate(Time = glue::glue("{startMonth} {startYear} -- {endMonth} {endYear}",.na = '')) |>
  select(Degree, Institution, Where, Time, advisor) |>
  gt() |> 
     opt_table_font(font = 'sans-serif') |> 
      tab_options(table.align = 'left',
                 table.font.size = '90%')#,
#                 container.width = 800)

```

<hr>

#### Teaching Experience

```{r}
work |> 
  filter(Academic == 'Yes') |>
  mutate(Time = glue::glue("{startMonth} {startYear} -- {endMonth} {endYear}",.na = '')) |> 
  select(title, organization, where, Time) |> 
    rename(Title = title, Organization = organization, Where = where) |> 
    gt() |> 
     opt_table_font(font = 'sans-serif') |> 
      tab_options(table.align = 'left',
                 table.font.size = '90%')#,
#                 container.width = 600)
 
```

<hr>

## Dashboards {.domain-header}

### Selected Applications

-   [Warehouse CITY](https://radicalresearch.shinyapps.io/WarehouseCITY/) - (2022 to Present)
-   [Annual Monitoring Network Plan Dashboard](https://radicalresearch.shinyapps.io/NetworkAssessment/)(2023 to present)
-   [Air Toxics Dashboard](https://radicalresearch.shinyapps.io/ToxicsDashboard/) - (2021)
-   [PM~2.5~ Data Quality Dashboard](https://sti-r-shiny.shinyapps.io/QVA_Dashboard/) - (2018 to Present)
-   [Ozone Data Quality Dashboard](https://sti-r-shiny.shinyapps.io/ozone_Dashboard/) - (2020 to Present)
-   [NO~2~ Data Quality Dashboard](https://sti-r-shiny.shinyapps.io/QVA_Dashboard/) - (2020 to Present)
-   [NCore Dashboard](https://sti-r-shiny.shinyapps.io/NCORE_Dashboard/) - (2020 to Present)

<hr> 

## Publications {.domain-header}

### Peer-reviewed articles


