---
title: "Services"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

-	**Atmospheric chemistry**: Hazardous air pollutants (air toxics), volatile 
organic compounds (VOCs), speciated particulate matter, near-road pollution
-	**Interactive dashboard development**: R Shiny, Rmarkdown, QMD, and API development
    + [WarehouseCITY dashboard](https://radicalresearch.shinyapps.io/WarehouseCITY/)
    + [EPA Annual Monitoring Network Plan Dashboard](https://rconnect-public.epa.gov/AMNP_Dashboard/)
    + [AirToxics dashboard](https://radicalresearch.shinyapps.io/ToxicsDashboard/)
    + [EPA NCore dashboard](https://sti-r-shiny.shinyapps.io/NCORE_Dashboard/)
    + [EPA PM FRM QA dashboard](https://sti-r-shiny.shinyapps.io/QVA_Dashboard/)
    + [EPA ozone QA dashboard](https://sti-r-shiny.shinyapps.io/ozone_dashboard/)
-	**Monitoring and network services**: Study design, network assessment, risk assessment,
community-scale monitoring, community engagement, fugitive dust, and litigation support
- **Statistical analysis**: Regressions, [source apportionment](https://www.fortair.org/wp-content/uploads/2022/04/Fort-Air-Partnership-Particulate-Matter-Speciation-Report-Final.html), hypothesis testing, cluster analysis, trend analysis, time-series analysis, geospatial analysis/GIS, distributions, model building, data mining
- **Quality assurance**: Quality management plans (QMPs),  Quality assurance project plans (QAPPs), and automated QA/QC algorithms
- **Training**: Statistics, R, atmospheric science, spatial mapping, [environmental data visualization](https://mikem-radicalresearch.quarto.pub/environmental-data-visualization/), and community-monitoring

```{r quals_processing, include=FALSE}

library(readxl)
library(tidyverse)
#import and process Qualifications table
quals_table <- read_excel('./images/quals2.xlsx', sheet = 'RR_LLC') %>%
  select(ProjectName,Client, Year, 'Atmospheric Chemistry', 'Dashboard', 'Monitoring and Network services',
         'Statistical Analysis',  'QA QC',  'Training') %>%
  arrange(desc(Year))

```

<hr>

```{r quals_table, layout="l-body-outset"}
#Display qualifications table
library(gt)

quals_table %>%
  mutate_at(c(2,4:9), ~replace_na(.,'')) %>% 
  gt() %>% 
  
  tab_header(
    title = 'Qualifications Table'
  ) %>% 
  data_color(
    columns = c(4:9),
    method = 'factor',
    palette = c('white', 'darkorange') 
  ) %>% 
  tab_style(
    style = list(
      cell_text(color = 'white', font = c('sans-serif', default_fonts()))
    ),
    locations = cells_body(
      columns = c(4:9),
      rows = everything()
    ) 
  ) %>% 
  cols_align(
    columns = c(4:9),
    align = 'center'
  ) |> 
  opt_table_font(font = 'sans-serif', weight = 8) |> 
  tab_options(table.align = 'left',
    table.font.size = '90%')
  
  
```


